\plaintitle

### 2016-08-19 drafts/labor/cases.tex
notes from meeting

\subsubsection{Achieving greater complexity}\label{sec:Complexity}
\topic{Crowdsourcing research has spent the better part of a decade attempting
to prove the viability of crowdsourcing in increasingly complex work.}  % this is my topic sentence.
\citeauthor{crowdForgeKittur}
map the discussion toward this goal in their work on
crowdsourcing complex work
\cite{crowdForgeKittur}.
\citeauthor{Lasecki:2013:CCC:2501988.2502057} tackle an area of computationally assisted interaction
--- conversational artificial intelligence ---
and find ways to arrange workers and formulate a ``crowd--powered conversational assistant''
\cite{Lasecki:2013:CCC:2501988.2502057}.
Other work has followed a similar pattern,
identifying target milestones in Computer Science
that have presented significant challenges for researchers,
and demonstrating that ``crowd--powered'' systems can tackle many of these challenges
with generally greater success than purely computational attempts
\cite[][and others]{Lasecki:2013:RCL:2441776.2441912,foundry}.

@@

\topic{We summarize the work discussed so far in this way:
researchers of crowdsourcing and on--demand labor in general
have attempted to find the characteristics which
enable and stymie successful applications of this form of work,
and how to get past or around these boundaries.}
Whether this work has focused on the self (as in the case of ``selfsourcing'')
or on others (as in \textit{CrowdForge} and \textit{Foundry}),
crowdsourcing literature has generally studied the constituent work
and attempted either to work around or indeed with the limitations of crowdwork to accomplish a difficult task
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016,crowdForgeKittur,foundry}.

% \topic{Research into piecework has also explored the limits of piecework,
% with some findings.}

>>>>

\subsubsection{Achieving greater complexity}\label{sec:Complexity}
\topic{Crowdsourcing research has spent the better part of a decade attempting
to prove the viability of crowdsourcing in increasingly complex work.}  % this is my topic sentence.
\citeauthor{crowdForgeKittur}
map the discussion toward this goal in their work on
crowdsourcing complex work
\cite{crowdForgeKittur}.
\ali{Types of things that people are trying to do that are complex: e.g. 1, e.g. 2, etc\dots}
\citeauthor{Lasecki:2013:CCC:2501988.2502057} tackle an area of computationally assisted interaction
--- conversational artificial intelligence ---
and find ways to arrange workers and formulate a ``crowd--powered conversational assistant''
\cite{Lasecki:2013:CCC:2501988.2502057}.
Other work has followed a similar pattern,
identifying target milestones in Computer Science
that have presented significant challenges for researchers,
and demonstrating that ``crowd--powered'' systems can tackle many of these challenges
with generally greater success than purely computational attempts
\cite[][and others]{Lasecki:2013:RCL:2441776.2441912,foundry}.

\ali{the thing that has made all of this possible has been decomposition and the application of computational processes (e.g. MapReduce) to make it all possible}

@@

\ali{
Nuke this:
\topic{We summarize the work discussed so far in this way:
researchers of crowdsourcing and on--demand labor in general
have attempted to find the characteristics which
enable and stymie successful applications of this form of work,
and how to get past or around these boundaries.}
Whether this work has focused on the self (as in the case of ``selfsourcing'')
or on others (as in \textit{CrowdForge} and \textit{Foundry}),
crowdsourcing literature has generally studied the constituent work
and attempted either to work around or indeed with the limitations of crowdwork to accomplish a difficult task
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016,crowdForgeKittur,foundry}.

Crowdforge, turkomatic, others talk about limiting factors; bring them up
}
% \topic{Research into piecework has also explored the limits of piecework,
% with some findings.}
